---
title: "faststi Calibration"
output: html_notebook
---

# General set-up

```{r "setup", include=FALSE}
knitr::opts_knit$set(root.dir = "~/dev/faststi")
library(tidyverse)
library(ggplot2)
```

Let's set up a function to create the parameter file for faststi, using
specified initial prevalences and infection probability parameters:

```{r}
initial_prevs <- function(msw_1550 = 0.01,
                          msm_1550 = 0.01,
                          wsm_1550 = 0.01,
                          wsw_1550 = 0.01) {
  return(as.list(environment()))
}

infection_parms <- function(inf_msw = 0.1,
                            inf_msm = 0.2,
                            inf_wsm = 0.05,
                            inf_wsw = 0.05) {
  return(as.list(environment()))
}

write_input <- function(name = "RTEST_", 
                        n_simulations = 100, 
                        n_agents = 10000, 
                        start_date = 2015, 
                        end_date = 2020,
                        analysis_step_days = 365,
                        n_threads = 4,
                        match_event = "CSPM", # CSPM / RKPM / BLOSSOMV
                        match_neighbours = 10,
                        match_clusters = 5,
                        prevs = initial_prevs(),
                        parms = infection_parms()) {
  # Write initial rates to file
  with(prevs, {
    initial_rates <- data.frame(AGE = c(14,19,24,29,34,39,44,49,100), # 14 - everyone up to 14.99999, 19 = 15-19.9999
                                MSW = c(0, rep(msw_1550,7), 0),
                                MSM = c(0, rep(msw_1550,7), 0),
                                WSM = c(0, rep(wsm_1550,7), 0),
                                WSW = c(0, rep(wsw_1550,7), 0))
    write.csv(initial_rates, "InitialRates.csv", row.names = FALSE, quote = FALSE)
  })
  # Write parameters to file
  with(parms, {
    lines <- ""
    simulation_name <- paste0(name, toString(inf_msw))
    line <- sprintf("SIMULATION_NAME %s\n", simulation_name)
    lines <- paste0(lines, line)
    lines <- paste0(lines, "NUM_SIMULATIONS ", n_simulations, "\n")
    lines <- paste0(lines, "NUM_AGENTS ", n_agents, "\n")
    lines <- paste0(lines, "NUM_THREADS ", n_threads, "\n")
    lines <- paste0(lines, "START_DATE ", start_date, "\nEND_DATE ", end_date, "\n")
    lines <- paste0(lines, "MATCH_EVENT ", match_event, "\n")
    lines <- paste0(lines, "MATCH_NEIGHBORS ",match_neighbours, "\n") # 
    lines <- paste0(lines, "MATCH_CLUSTERS ", match_clusters, "\n") #
    lines <- paste0(lines, "ANALYZE_DURING_SIM ", analysis_step_days, "\n")
    lines <- paste0(lines, "HET_MALE_INFECTIOUSNESS ", inf_msw, "\n")
    lines <- paste0(lines, "HOM_MALE_INFECTIOUSNESS ", inf_msm, "\n")
    lines <- paste0(lines, "HET_FEMALE_INFECTIOUSNESS ", inf_wsm, "\n")
    lines <- paste0(lines, "HOM_FEMALE_INFECTIOUSNESS ", inf_wsw, "\n")
    lines <- paste0(lines, "BREAKUP_EVENT LIMIT\nMATING_POOL_EVENT LIMIT\n")
    lines <- paste0(lines, "INITIAL_INFECTION_RATES_CSV InitialRates.csv")
    write(lines, file="FaststiInput.txt")
  })
}

```

Now let's set up a function that runs the simulation the specified number of times
(with true stochasticity or a specified seed.

```{r}
faststi_simulation <- function(seed = 123, param.set) {
  # This is an ugly workaround for the fact that EasyABC only allows parameters
  # for which priors are set
  fixed <- get("fixed_params",env=globalenv())
  
  with(fixed, {
    write_input(n_simulations = n_simulations,
                n_agents = 10000,
                start_date = start_date,
                end_date = end_date,
                prevs = prevs,
                parms = infection_parms(inf_msw = param.set[1],
                                        inf_msm = param.set[2],
                                        inf_wsm = param.set[3],
                                        inf_wsw = param.set[4]))
  })
  #time <- toString(lubridate::now())
  #outfilename <- paste0("FaststiOutput_",gsub(" ","_",gsub(":","-",time)),".csv")
  outfilename <- "FaststiOutput.csv"
  cmd = sprintf("./faststi -s %i -f %s >%s", seed, "FaststiInput.txt", outfilename)
  system(cmd)
  results <- read.csv(outfilename, TRUE)
  final_prevalences <- dplyr::filter(results, Desc2 == "PREVALENCE", Date == max(Date))
  mean_final_prevalence = mean(final_prevalences$Value)
  sd_final_prevalence = sd(final_prevalences$Value)
  browser()  
  years <- unique(results$Date)[3:length(unique(results$Date))-1]
    mean_prevs <- vector(length = length(years))
    for (i in 1:length(years)) {
      mean_prevs[i] <- mean(dplyr::filter(results, Desc2 == "PREVALENCE", Date == years[i])$Value)
    } 
  print(paste0("Mean final prevlances: ", mean_final_prevalence))
  print(paste0("SD final prevlances: ", sd_final_prevalence))
  return(mean_prevs)
}
```

Now let's test it with 64 runs (4 threads), using a seed value and default
parameter values:

```{r}
fixed_params <-  list(n_simulations = 64,
                      n_threads = 4,
                      start_date = 2015,
                      end_date = 2020,
                      prevs = initial_prevs())
true_params <- unlist(infection_parms())
sim.output <- faststi_simulation(seed = 124, param.set = true_params)
print(sim.output)
```

Now, let's simulate a dataset from these values:

```{r}

```